|

### 2024-07-01 manuscript.Rmd
Fixed another osf download bug

for (f in 1:length(filelist)){
  if (!file.exists(paste0('local/',filelist[f]))){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject)
  fid <- which(osffiles$name==filelist[f])
  osf_download(osffiles[fid,], path='local/',progress=TRUE)}
}

@@

  if (!file.exists('local/GroupDataRobots.RData')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject)
  fid <- which(osffiles$name=='GroupDataRobots.RData')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)}

@@

  if (!file.exists('local/GroupDataMasks.RData')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject)
  fid <- which(osffiles$name=='GroupDataMasks.RData')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)}

>>>>

for (f in 1:length(filelist)){
  if (!file.exists(paste0('local/',filelist[f]))){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject,n_max=100)
  fid <- which(osffiles$name==filelist[f])
  osf_download(osffiles[fid,], path='local/',progress=TRUE)}
}

@@

  if (!file.exists('local/GroupDataRobots.RData')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject,n_max=100)
  fid <- which(osffiles$name=='GroupDataRobots.RData')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)}

@@

  if (!file.exists('local/GroupDataMasks.RData')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject,n_max=100)
  fid <- which(osffiles$name=='GroupDataMasks.RData')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)}
